Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-08-26 article/article.tex
Commit 2024-08-25 19:11
Commit 2024-08-26 09:08

Following the application of the above discussed methodology to the
entire dataset (\(6.1\) million of one-minute GHI measurements),
\(1.76\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
events. The highest recorded GHI due to CE was
\(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007, corresponding to OI of
\(345.9\,\text{W}/\text{m}^2\). The strongest CE event of \(49.7\,\%\)
above the clear sky threshold was observed on 28~October 2016. In the
following sections we are discussing the long-term trends and
variability of the CE events as well as of the corresponding OI and
excess irradiation.

>>>>

Following the application of the above discussed methodology to the
entire dataset (\(6.1\) million of one-minute GHI measurements),
\(1.76\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
events. The highest recorded GHI due to CE was
\(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007 at a SZA of
\(19.9^\circ\) corresponding to OI of \(345.9\,\text{W}/\text{m}^2\) or
\(32.3\,\%\) above the threshold. The strongest CE event of \(49.7\,\%\)
above the clear sky threshold was observed on 28~October 2016 at a SZA
of \(59.2^\circ\) with a GHI value of \(861.8\,\text{W}/\text{m}^2\) and
a OI of \(286.1\,\text{W}/\text{m}^2\). Both cases are ECE events with
\(168.7\,\text{W}/\text{m}^2\) and \(155.4\,\text{W}/\text{m}^2\) above
the TSI at TSI for the same SZA, respectively. In the following sections
we are discussing the long-term trends and variability of the CE events
as well as of the corresponding OI and excess irradiation.
